\section{User Evaluation}\label{sec:userevaluation}

As a team we were advised by our project manager to perform preliminary, in-house user tests before the Project Discovery game would be showcased at EVE Vegas, a conference for EVE Online players and fans. The purpose of this test was to shed light on any obvious errors with the game, especially the tutorial phase which was at an early stage.

\subsection{Implemention}
The tests took place on the 9th of October. We got five volunteers from CCP, four males and one female between the ages of 25 to 40. The people were a mix of game designers, quality assurance people and a community developer. The reason we only got people from within CCP to partake in the tests was that the game was not ready to be revealed to the public so we could not get people outside of CCP to perform the test.

The test was performed on a computer that remotely connected to our personal work desktop. When a tester arrived, we greeted them, thanked them for coming, and explained the procedure. The procedure was that the tester would sit down and we would observe them while they played. The player would open Project Discovery, finish the tutorial and a handful of other tasks. While playing, the tester would verbally express their thoughts, for us to write down. Testers could play for as long as they wanted, given that they continued to think aloud.

After the tester had finished playing we asked them questions about their experience playing the game and then thanked them for their contribution to the project.

\subsubsection{Data}

In this section we outline the data received from each of the testers, this data is comprised of a list of questions we asked the testers after the test was performed, and their answers.

\begin{table}[H]
\centering
\caption{The first question}
\label{tab:question1}
\begin{tabular}{p{1.3cm}p{10cm}}
\toprule
 & \multicolumn{1}{c}{Did you find the tutorial helpful?} \\ \midrule
Tester 1 & \multicolumn{1}{c}{NA} \\
Tester 2 & Yes, but it was way too simple compared to the real game. \\
Tester 3 & No, I breezed through it and didn't pay attention to it. \\
Tester 4 & Yes, I liked it. \\
Tester 5 & Yes, but I felt that it didn't scale up in difficulty enough. \\ \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{The second question}
\label{tab:question2}
\begin{tabular}{p{1.3cm}p{10cm}}
\toprule
 & \multicolumn{1}{c}{Did you understand the aim of the game?} \\ \midrule
Tester 1 & Yes. \\
Tester 2 & Yes. \\
Tester 3 & No. \\
Tester 4 & Yes. \\
Tester 5 & Yes. \\ \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{The third question}
\label{tab:question3}
\begin{tabular}{p{1.3cm}p{10cm}}
\toprule
 & \multicolumn{1}{c}{Did you feel a sense of accomplishment when you were correct?} \\ \midrule
Tester 1 & Sure, it's pretty hard to get it right, but rewarding when you do. \\
Tester 2 & It's okay, I thought the result screen could show some more fanfare if you are correct. \\
Tester 3 & I did not feel accomplished. \\
Tester 4 & Yes! \\
Tester 5 & Yeah totally! It's always fun to be 100\% correct. \\ \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{The fourth question}
\label{tab:question4}
\begin{tabular}{p{1.3cm}p{10cm}}
\toprule
 & \multicolumn{1}{c}{Do you think the interface was easy to understand?} \\ \midrule
Tester 1 & Yes, but the color selection channels were not explained, so I didn't know what they were for. \\
Tester 2 & Yes. \\
Tester 3 & Yes. \\
Tester 4 & Sure, I think it could have been explained a little more though. \\
Tester 5 & Yes. \\ \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{The fifth question}
\label{tab:question5}
\begin{tabular}{p{1.3cm}p{10cm}}
\toprule
 & Did you feel a sense of excitement when waiting to see if your answer was correct? \\ \midrule
Tester 1 & Yes. \\
Tester 2 & Yes. \\
Tester 3 & Yes. \\
Tester 4 & Yes. \\
Tester 5 & Yes. \\ \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{The sixth question}
\label{tab:question5}
\begin{tabular}{p{1.3cm}p{10cm}}
\toprule
 & \multicolumn{1}{c}{Any thoughts or comments?} \\ \midrule
Tester 1 & Overall I thought it was really great, just a bit confusing at first. \\
Tester 2 & The tooltips were too long and technical, so I ignored them. I really would have liked to be able to zoom in on the main image. \\
Tester 3 & I would like a better tutorial, more information on what I should have been doing. \\
Tester 4 & I would like a zoom feature for the images. \\
Tester 5 & A zoom function would have been great, and simpler tutorial tooltips. \\ \bottomrule
\end{tabular}
\end{table}


\subsection{Results}

In this section we analyze the data derived from the tests and how we used that data to come up with improvements for the game.

\subsubsection{Tooltips}
Proper use of tooltips is paramount to the players understanding, players seemed to be confused about their role in the game. We need tooltips to be clear and helpful to players understanding the interface. To this end, tooltips should be utilized not only at the first opening of the interface, but also throughout the whole tutorial \& training session, gradually teaching players about the game as they face the actual problems. The tooltips also need to be shorter and should always focus on one specific message. Testers did not immediately grasp that they could change the colour filter on the main image, we need to add a tooltip that describes this functionality. All in all the tooltips were not descriptive enough, and testers felt that there were not enough of them.

\subsubsection{Tutorial}
Testers felt that the tutorial was too easy and did not teach them very much about the real game. To rectify this, we are planning to implement a more extensive tutorial, where each image teaches the player a specific attribute of the game. Whether that lesson is about the interface, or how to classify certain patterns in images. 

Testers expressed the need for an explanation after each tutorial task, so we will contact the Human Protein Atlas about getting explanations for each training task, to explain why the correct solution was correct.

\subsubsection{Interface}
Testers did not have much to say about the interface except that they would have liked to have a zoom option on the main image, and to rectify this, we are going to implement a magnification feature on the main image.

We observed testers, who had completed the training phase, and were contributing to unknown tasks, did not get a result screen. That is normal behaviour since the solution is unknown, we can not reliably give a result. We saw that when users weren't getting instant feedback they were not as interested and seemed less motivated to find the right solution to the tasks. Our solution to this problem was that since we do know the community consensus for specific tasks at any given time, we can show exact percentages for choices by other players. We felt that since testers expressed excitement in seeing a result screen, we should implement this for unknown tasks, so that the game would not lose the factor of excitement once players reach the stage of solving images that have no known solution. This could be a major improvement in the enjoyment players experience while playing the game.