\section{Tools and facilities}\label{tools}

\subsection{Facilities}
All of the work on the project will take place at CCP headquarters at Grandagarður 8. Both team members have been assigned work stations close to each other for the duration of the project. The work stations include all the tools needed to complete the project. 

\subsection{Tools for the game itself}
We will be using Perforce for Version control. The reason for that is simple, it's the version control system used at CCP. The programming language we will use is Python, again because that's what CCP use to code EVE Online. The integrated development environment (IDE) we intend to use is PyCharm, it integrates very well with Perforce and is widely used at CCP. For code reviews we will use Code Collaborator which is also used at CCP.

\subsection{Tools for the website}
We will use Perforce for version control for the website as well as the game. The website will be done in HTML5 as we want it to have a modern look and functionality. For all the scripting purposes of the site we will use Javascript as it has universal browser support and we have the most experience using it. We will be using the React Javascript library to build the user interface. It will limit rendering of objects as it only renders objects that change and it will allow us to have reusable components which will simplify the process. To help us keep the Javascript code quality in check we will be using JSHint. For styling the website we will use Less, which will allow us to have shorter and cleaner code. The IDE we are going to use for all the aforementioned languages is Sublime Text, we both have experience using it and feel comfortable with it. 

We will use Bower to keep track of packages and dependencies for the website. For unit testing we will use Jasmine as our test framework and Karma as our test runner. We will use Grunt as our task runner to run various tasks such as JSHint checking, running unit tests, minifying and concatenating the code, each time we change the code.

\subsection{Other tools}

All of the reports related to the project will be done using \LaTeX. We will be using Toggl to keep track of the total time spent on the project and on individual tasks. To keep track of our Scrum progress, we will be using Jira, which is used within CCP for that purpose.