\section{Expected outcome}\label{sec:expected_outcome}

Two main outcomes are expected by the end of the project. One is to implement the remaining features of \emph{Project Discovery}, and launch it on the \emph{EVE Online} test server, \emph{Singularity}. The other is to develop and launch a website dedicated to \emph{Project Discovery} that details its progress and player statistics, as well as informs the players and general public about it.\\

These are the main remaining features that we expect to be able to finish for this project:
\begin{itemize}
  \item A training phase where players get easy tasks and a few categories to solve.
  \item A detailed rewarding system, where players complete daily challenges for further rewards.
  \item A leaderboard, where players compete to be the best of the best.
  \item A detailed view of the history of player submissions, where each player can see what submission changed their score.
\end{itemize}

We also need to clear up a few things regarding authorization, optimization, player statistics tracking and how our client will be able to connect to the external MMOS API.\\

After release on the test server (or before, it is undecided), our task is to develop a website to launch along with the mini-game. At this point no development or design has been done on the website and only very basic discussion has taken place on the content of it, so the web development part of the project is likely to change and expand in scope. What we know currently is that it will contain information about \emph{Project Discovery} and it will in some way show the progress the \emph{EVE} players are making with the research, for an example how many pictures have been analyzed and how many more need to be analyzed.
